Quantifying the importance of a tree prior in Bayesian phylogenetics

### 2019-04-15 article.tex
Put creation of experiments in code
Describe burn-in better, thank @Giappo

The fourth step quantifies the inference error made.
It creates an error distribution, by measuring the difference
between the true tree and each of the posterior 
trees (Fig.~\ref{fig:pipeline}, 4a $\rightarrow$ 5a).
The default way to quantify the difference between two phylogenies
is the nLTT statistic (\cite{janzen2015approximate}), but any 
user-defined error statistic can be used.
The error statistic is not applied on all posterior phylogenies 
\giovanni{How is the MCMC topic connected to what previously said?} 
XXXXXXXXXXXXXXXXXXXXXXXXXXXX33
An MCMC needs to 'warm up', as initially it will sample
an unrepresentative part of state space. This phase, called 
the burn-in, is commonly set up to be a small part of the entire run, 
after which it is discarded. By default, \verb;pirouette; 
uses a cut-off value of 10\%.

@@

YYYYYYYYYYYYYYYYYYYYYYYYYYYYYYYY
experiments <- list(experiment)

@@

We specify that we want all 40 inference models to compete 
by calling \verb;create_all_experiments;,
as we previously did in listing~\ref{lst:create_all_experiments}.

We choose again to use the default error measurement setup,
as shown in listing~\ref{lst:create_error_measure_params}.

To get an idea of a baseline error made by BEAST2, 
we also make use of the twinning option by using
the same pir\_params XXXXXXXXXXXXXXXXXXXXXXXXXXXx as shown in 
listing~\ref{lst:create_pir_params_with_twinning}.
We run \verb;pirouette; (listing~\ref{lst:pir_run}) 
and plot the results (listing~\ref{lst:pir_plot}).
The output is shown in figure~\ref{fig:example_4}.

@@

We choose again to use the default error measurement parameters
created in listing~\ref{lst:create_error_measure_params},
with twinning, as alsready shown in 
listing~\ref{lst:create_pir_params_with_twinning}. XXXXXXXXXXXXXXXXXXXXX

>>>>

The fourth step quantifies the inference error made, by removing
the burn-in, then applying an error statistic.
The burn-in is the first phase of the MCMC,
where it samples an unrepresentative part of state space,
and is commonly discarded. By default, \verb;pirouette; 
uses removes the first 10\% of the posterior.
From the remaining posterior, \verb;pirouette; 
creates an error distribution, by measuring the difference
between the true tree and each of the posterior 
trees (Fig.~\ref{fig:pipeline}, 4a $\rightarrow$ 5a).
The default way to quantify the difference between two phylogenies
is the nLTT statistic (\cite{janzen2015approximate}), but any 
user-defined error statistic can be used.

@@

\begin{lstlisting}[
  language=R, 
  floatplacement=ht, 
  frame=single,
  label = {lst:create_experiments},
  caption = Create a list of one experiment.
]
experiments <- list(experiment)
\end{lstlisting}

@@

We specify that we want all 40 inference models to compete 
by calling \verb;create_all_experiments;,
as we previously did in listing~\ref{lst:create_all_experiments}.
We choose again to use the default error measurement setup,
as shown in listing~\ref{lst:create_error_measure_params}.
To get an idea of a baseline error made by BEAST2, 
we also make use of the twinning option by using
the same call to \verb;create_pir_params; as shown in 
listing~\ref{lst:create_pir_params_with_twinning}.
We run \verb;pirouette; (listing~\ref{lst:pir_run}) 
and plot the results (listing~\ref{lst:pir_plot}).
The output is shown in figure~\ref{fig:example_4}.

@@

We choose again to use the default error measurement parameters
created in listing~\ref{lst:create_error_measure_params}.
We enable twinning, by calling \verb;create_pir_params;
as shown in listing~\ref{lst:create_pir_params_with_twinning}.
